The Size Distribution of Firms and Industrial Water Pollution \\ A Quantitative Analysis of China

### 2019-09-19 Documentation/Pollution_Final_AEJ_Template.tex
ready for submission

% Article Format: American Economic Review
% Xin Tang @ Stony Brook University
% Last Updated: August 2014
\documentclass[twoside,12pt,leqno]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                    Text Layout                       %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Page Layout
\usepackage[hmargin={1.2in,1.2in},vmargin={1.5in,1.5in}]{geometry}
\topmargin -1cm        % read Lamport p.163
\oddsidemargin 0.04cm   % read Lamport p.163
\evensidemargin 0.04cm  % same as oddsidemargin but for left-hand pages
\textwidth 16.59cm
\textheight 21.94cm
\renewcommand\baselinestretch{1.15}
\parskip 0.25em
\parindent 1em
\linespread{1}

% Set header and footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[LE,RO]{\thepage}
%\fancyhead[CE]{\textit{JI QI, XIN TANG AND XICAN XI}}
%\fancyhead[CO]{\textit{THE SIZE DISTRIBUTION OF FIRMS AND INDUSTRIAL POLLUTION}}
\cfoot{}
\renewcommand{\headrulewidth}{0pt}
%\renewcommand*\footnoterule{}
%\setcounter{page}{1}

% Font
\renewcommand{\rmdefault}{ptm}
\renewcommand{\sfdefault}{phv}
%\usepackage[lite]{mtpro2}
% use Palatinho-Roman as default font family
%\renewcommand{\rmdefault}{ppl}
\usepackage[scaled=0.88]{helvet}
\makeatletter   % Roman Numbers
\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother
\usepackage{CJK}

% Section Titles
\renewcommand\thesection{\textnormal{\textbf{\Roman{section}.}}}
\renewcommand\thesubsection{\textnormal{\Alph{subsection}.}}
\usepackage{titlesec}
\titleformat*{\section}{\bf \center}
\titleformat*{\subsection}{\it \center}
\renewcommand{\refname}{\textnormal{REFERENCES}}

% Appendix
\usepackage[title]{appendix}
\renewcommand{\appendixname}{APPENDIX}

% Citations
\usepackage[authoryear,comma]{natbib}
\renewcommand{\bibfont}{\small}
\setlength{\bibsep}{0em}
\usepackage[%dvipdfmx,%
            bookmarks=true,%
            pdfstartview=FitH,%
            breaklinks=true,%
            colorlinks=true,%
            %allcolors=black,%
            citecolor=blue,
            linkcolor=red,
            pagebackref=true]{hyperref}

% Functional Package
\usepackage{enumerate}
\usepackage{url}      % This package helps to typeset urls

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                    Mathematics                       %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathrsfs,upgreek}
% Operators
\newcommand{\E}{\mathbb{E}}
\newcommand{\e}{\mathrm{e}}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\plim}{plim}
\renewcommand{\vec}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\gvec}[1]{{\boldsymbol{#1}}}

% New Environments
\newtheorem{result}{Result}
\newtheorem{assumption}{Assumption}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\setlength{\unitlength}{1mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                 Tables and Figures                   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{threeparttable,booktabs,multirow,array} % This allows notes in tables
\usepackage{floatrow} % For Figure Notes
\floatsetup[table]{capposition=top}
\usepackage[font={sc,footnotesize}]{caption}
\DeclareCaptionLabelSeparator{aer}{---}
\captionsetup[table]{labelsep=aer}
\captionsetup[figure]{labelsep=period}
\usepackage{graphicx,pstricks,epstopdf}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Begin Document Content %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{\vspace{-1cm}\Large{{\textsf{The Size Distribution of Firms and Industrial Water Pollution\\A Quantitative Analysis of China}}}\thanks{Disclaimer: The results and conclusions in this paper are those of the authors, and do not necessarily reflect the views of the China Ministry of Environmental Protection, or those of the International Monetary Fund. An online appendix containing additional materials is available on the author's website: {\color{blue}https://sites.google.com/site/zjutangxin/}.}}
\author{\normalsize{\textit{By}\ \textsc{Ji Qi},\ \textsc{Xin Tang},\textsc{\ and\ }\textsc{Xican Xi}}\thanks{Qi: Chinese Academy for Environmental Planning, Room 709-B BeiKeChuangYe Tower, No.10 Dayangfang, Beiyuan Road, Beijing, China, 100012 (e-mail: qiji@caep.org.cn); Tang: Wuhan University and International Monetary Fund, 700 19th St NW, Washington D.C., United States, 20431 (e-mail:zjutangxin@gmail.com); Xi: School of Economics, Fudan University, 600 Guoquan Road, Shanghai, China, 200433 (e-mail:xicanxi@fudan.edu.cn). We are grateful for the comments from Alexis Anagnostoupolos, Marina Azzimonti, Juan Carlos Conesa, Berthold Herrendorf, Nicolai Kuminoff, Pietro Peretto, Edward Prescott, Diego Restuccia, Todd Schoellman, Kerry Smith, Daniel Yi Xu, Gustavo Ventura, the editor and three anonymous referees. We also benefited from the comments received at Arizona State University, the Chinese Academy of Environmental Planning, Duke University, the IMF, U.S International Trade Commission, Peking University, Shanghai University of Finance and Economics, Singapore Management University, Stony Brook University, Washington State University, Wuhan University, and Zhejiang University. We sincerely thank the China Ministry of Ecology and Environment for granting us access to the National General Survey of Pollution Sources data. This paper has been screened to ensure that no confidential data are revealed.}} %The authors declare that they have no relevant or material financial interests that relate to the research described in this paper.}}
\date{\textnormal{\today}}

\begin{document}
\maketitle
%\renewcommand{\abstractname}{}
\vspace{-1.5em}
%\begin{abstract}
\begin{center}
\begin{minipage}[c]{0.8\textwidth}
{%\normalsize
%\noindent \textit{We study the role of firm-size distribution in industrial pollution using a quantitative model featuring a distribution of firms. Micro-level data support a negative correlation between firm size and polluting intensity. Fixed costs associated with advanced treatment technologies are shown to be important in explaining the negative size-intensity correlation. Evidence suggests that product market frictions limit the expansion of productive firms in China, which leads to survivals of unprofitable small polluting firms. Quantitative analysis using a model consistent with these empirical regularities shows that while having moderate effect on output, size distribution exerts considerable effect over industrial pollution. (\textit{JEL} E01, E23, O44, Q52, Q53, Q56)}
\noindent \textit{We argue that misallocation across firms amplifies industrial water pollution by distorting the firm size distribution in China. Firm-level data indicate that larger firms are more likely to use clean technology but face higher distortions. In a heterogeneous firms model with an endogenous choice of pollution treatment technologies, we show that distortions that increase with firm-level TFP lower the adoption of clean technology, amplify aggregate pollution intensity, and lower aggregate output. Quantitatively, eliminating these correlated distortions would increase output by 30\% and decrease pollution by 20\%. Meanwhile, environmental regulations have sizable impact on pollution but only limited effect on output. (JEL E23, L11, O44, Q52, Q53, Q56)}}
\end{minipage}
\end{center}

\textnormal{Severe} pollution has accompanied China's remarkable economic growth in the past few decades, causing environmental degradation, public health damage, and millions of premature deaths.\footnote{\citet{WorldBank_Cost_2007} estimates that the cost of air and water pollution in China is about 6\% of GDP. The health cost of pollution is estimated to be 4\% of GDP, the majority of which is associated with premature deaths caused by pollution. %\citet{Ebenstein:2012} finds that industrial water pollution has a large effect on deaths from digestive cancers in China, while \citet{Ebensteinetal:2015} show that air pollution is negatively associated with life expectancy.
See \citet{Vennemoetal:2009} and \citet{ZhengKahn:2013} for review of empirical studies on environmental pollution in China.} %Therefore it has become a major concern for both the public and policymakers. %\footnote{The Chinese government has initiated a campaign against pollution. According to the \textit{Report on the Work of the Government 2014}, the State Council has allocated \$600 billion of special funds to reduce air and water pollution during the Thirteenth Five-Year Plan (2016-2020).}
Understanding the driving forces behind this severe pollution is crucial for designing and evaluating anti-pollution policies. An outstanding question is whether the severe pollution is an inevitable consequence of rapid economic growth, or largely exacerbated by policy distortions and/or market inefficiencies.

In this paper, we argue that misallocation across firms amplifies industrial water pollution by distorting the firm size distribution in China. Using nationally representative data on firm production, pollution emissions and pollution treatment technologies, we document two facts on firm size and pollution intensity (pollutants per output) in China.\footnote{We use the \textit{National General Survey of Pollution Sources} (NGSPS) and \textit{National Economic Census} (CNEC) in China. Section \rom{1} provides more details.} First, large firms have lower pollution intensity than small firms, with an elasticity of $-$0.37 between firm size and pollution intensity for the top five polluting industries in China.\footnote{The industries are ranked by their emissions of \textit{Chemical Oxygen Demand} (COD). The five industries are (with two-digit GB/T4547-2002 code in parentheses): Paper and Paper Products (C22), Processing of Food from Agricultural Products (C13), Textiles (C17), Raw Chemical Materials and Chemical Products (C26), and Beverages (C15).} % We find 7- to 32-fold differences in pollution intensity between firms in the largest and smallest quartiles of the firm size distribution for the top five polluting industries in China.
Furthermore, we find that this is not only due to fewer pollutants per output are generated by large firms during production, but also that large firms are also more likely to use advanced end-of-pipe treatment technologies that require sizable fixed installation costs. %\footnote{The negative correlation between firm size/productivity and pollution intensity has also been found in other countries. For example, for developing countries \citet{Dasguptaetal:1998} find that small firms have higher air pollution intensity in Brazil and Mexico, and \citet{Martin:2013} and \citet{BarrowsOllivier:2016} find that smaller firms have higher energy intensity in India. For developed countries, \citet{Bloometal:2010} find that better managed firms have lower energy intensity in the United Kingdom, and \citet{ShapiroWalker:2015} find that more productive firms have lower pollution intensity in the United States. However, the richness of our data allows us to establish empirically a unique link between firm size and the adoption of clean technology, and thus to provide a mechanism for this negative correlation that is observable.}\textsuperscript{, }
%\footnote{Our data reveal that large firms are more likely to not only use advanced \textit{end-of-pipe} treatment technologies to remove a larger proportion of pollutants, but also generate less pollutants in production. This could be because that the production technologies used by large firms are also more environmentally friendly, or also because they are using less inputs. While we cannot directly observe firms' production technologies, we do have data on firms' end-of-pipe pollution treatment technologies.}
Second, large firms account for a smaller proportion of the total employment in China than in the United States. For the top five polluting industries in China, firms with more than 400 employees account for 20\% of the total employment compared with close to 70\% for the U.S. counterparts. %\footnote{See \citet{Axtell:2001}, \citet{Luttmer:2007}, and \citet{RossihansbergWright:2007} for theories and evidence regarding the heavy right tail of the U.S. firm and establishment distributions.}
If we take the U.S. economy as a less distorted benchmark, these facts suggest that distortions to firm size distribution could have important environmental consequences in China. %This fact is suggestive of the size-dependent distortions that reallocate factors away from large productive firms in China if we take the U.S. economy as a relatively distortion-free benchmark. Indeed, we find that in China, the average product of labor and capital increase strongly with firm size and productivity [\citet{HsiehKlenow:2009, HsiehKlenow:2014}].\footnote{This measure of distortion captures the effects of many of the factors that distort factor allocation across firms, including taxes and subsidies, regulations, local protectionism, transportation costs, and financial frictions. A prominent example of such size-dependent distortions is internal trade barriers that impede the flow of goods across regions, which presumably affect large firms more since these are more likely to sell goods across regions [\citet{Young:2000}, \citet{TombeZhu:2015}, and \citet{Eberhardtetal:2016}]. In addition, as is the case in many other developing countries, small firms are more likely to evade taxes because of imperfect tax enforcement.}
%Formally, we follow the approach developed by \citet{HsiehKlenow:2009, HsiehKlenow:2014}, and estimate distortions that affect factor allocation across firms using firm-level variations in average products of capital and labor. We find that firm-level distortions increase with firm size and productivity, consistent with the fact that large firms account for a smaller fraction of total employment in China.\footnote{It is well understood in the literature that this measure of distortions captures the effects of many factors that distort factor allocation across firms, including taxes and subsidies, regulations, transportation costs and financial frictions, among others. A prominent example of such size-dependent distortions is internal trade barriers that impede the flow of goods across regions, which presumably affect large firms more, since they are more likely to sell goods across regions. \citet{TombeZhu:2015} find that the internal trade barriers have a large impact on China's aggregate productivity. In addition, as is the case in many other developing countries, small firms are more likely to evade taxes due to imperfect tax enforcement.}

Motivated by these facts, we build a two-sector (polluting and non-polluting) model of heterogeneous firms based on \citet{Lucas:1978b} to evaluate how firm-level distortions affect aggregate output and pollution. The model has the following key features. First, firms in each sector differ in their productivity levels. There is a stand-in household with a continuum of members, and each member draws a sector specific managerial ability from a given distribution. When members choose to be manager, they enter the sector their managerial ability belongs to and the ability determines the TFP of the firm they run. Second, firms differ in pollution intensity as well. As in \citet{CopelandTaylor:1994}, pollution emissions are a by-product of production for firms in the polluting sector. Following Fact 1 above, we assume that generated emissions per output during production is decreasing in firm output.\footnote{While our data reveal that large firms generate fewer pollutants per output, we do not know precisely the reasons behind that. %It may be because large firms use fewer or cleaner inputs to produce the same amount of output. For example, \citet{Bloometal:2010} find that better managed firms use less energy to produce the same amount of output in the U.K.. As another example, the paper pulp industry in China uses two different types of inputs: bagasse and wood. While bagasse, which generates 140--180 kg COD per ton, is mostly used by firms with an annual production of {\color{black}less} than 100 k-tons, wood, which generates 30--55 kg COD per ton, is mostly used by firms with an annual production of {\color{black}more} than 100 k-tons.
Without further data, we model the emissions generated during production in a reduced-form way, which is then calibrated to the data. Section \rom{1}.B discusses this point in more details.} Third, firms have the option to adopt an advanced end-of-pipe treatment technology, which we refer to as \textit{clean} technology later, after paying a fixed adoption cost. Firms in the polluting sector are subject to environmental regulations such that firms that do not use the clean technology face a penalty that takes away a fraction of their profits. %\footnote{In reality, a powerful tool used by the Chinese government to enforce environmental regulations, is to randomly audit and then shut down firms that do not comply with environmental regulations for a certain period of time, which would cost these firms a fraction of their profits. See for example, Trevor Nace, ``China shuts down tens of thousands of factories in widespread pollution crackdown,'' Forbes, October 2017.} % (\url{https://www.forbes.com/sites/trevornace/2017/10/24/china-shuts-down-tens-of-thousands-of-factories-in-widespread-pollution-crackdown})
As a result, our model predicts that only firms above a certain size threshold would choose the clean technology, which is qualitatively consistent with the fact that large firms are more likely to use clean technology.

Finally, we assume that firms face distortions that increase with their TFP, or \emph{correlated} distortions following the terminology of \citet{RestucciaRogerson:2008}, which are modeled as progressive output taxes.\footnote{\citet{Guneretal:2008} study a closely related type of distortions, namely \emph{size-dependent} distortions, which increase with firm or establishment size (the amount of capital, labor or output). An example is the many labor regulations in Italy, Spain and France that start to bind on firms with more than a certain number of employees. Both correlated and size-dependent distortions lead to a reallocation of resources from high TFP to low TFP firms, and they are essentially equivalent when distortions do not lead to rank reversal defined as more productive firms being smaller [\citet{Hopenhayn:2014}].} We find in our data that firms with higher TFP exhibit substantially higher average products of capital and labor in both the polluting and non-polluting sectors, indicating that more productive firms do face higher distortions [\citet{HsiehKlenow:2009, HsiehKlenow:2014}]. %\footnote{Pioneered by \citet{HsiehKlenow:2009, HsiehKlenow:2014}, this approach to measure distortions captures the effects of a number of factors that distort factor allocation across firms, including taxes and subsidies, regulations, local protectionism, transportation costs, and financial frictions. A prominent example of correlated distortions is internal trade barriers that impede the flow of goods across regions, which presumably affect large productive firms more since these are more likely to sell goods across regions [\citet{Young:2000}, \citet{TombeZhu:2015}, and \citet{Eberhardtetal:2016}]. In addition, as is the case in many other developing countries, small firms are more likely to evade taxes because of imperfect tax enforcement.}
As emphasized by previous studies, such as \citet{RestucciaRogerson:2008} and \citet{HsiehKlenow:2014}, correlated distortions lower both mean firm size and aggregate output, since they limit the operations of productive firms and allow too many unproductive firms to survive and expand. %\footnote{See \citet{RestucciaRogerson:2008}, \citet{Bartelsmanetal:2013}, \citet{HsiehKlenow:2014}, \citet{AdamopoulosRestuccia:2014}, \citet{BentoRestuccia:2016} among many others.}
A new insight from our model is that correlated distortions also increase aggregate pollution intensity for two reasons. First, they lower the profits of productive firms which reduces their incentives to adopt the clean technology. Therefore fewer firms adopt clean technology in the equilibrium with correlated distortions. Second, they take production factors away from large productive firms that also have lower pollution intensity, which drives up the average pollution intensity further.

%When connecting our model with firm-level data, we are able to quantify the aggregate effects of correlated distortions in a comprehensive way, taking into account the general equilibrium responses. Specifically, we can assess structurally the three channels through which distortions affect aggregate pollution, following the convention in environmental economics: scale (change in aggregate output), composition (reallocation across sectors), and technique (change in sectoral pollution intensity).\footnote{See, for example, \citet{GrossmanKrueger:1993}, \citet{CopelandTaylor:2004}, and \citet{Levinson:2009}, among others.} Moreover, our model and data allow us to further decompose the technique effect into: within sector reallocation across firms, and the change in the adoption of clean technology.

@@

To discipline our quantitative analysis, we calibrate our model to match the observed pollution intensity, the adoption of clean technology, the correlation between distortions and firm TFP, and the firm size distribution in the Chinese data. We map the polluting sector to the top five polluting industries mentioned above, which account for 80\% of the total emissions in the data, and map the non-polluting sector to the rest of the manufacturing sector. We then use the calibrated model to evaluate the effects of two policies: removing correlated distortions from both sectors and strengthening environmental regulations.\footnote{Here we follow the so-called \emph{indirect} approach in the study of misallocation [\citet{RestucciaRogerson:2013}] by quantifying the overall effects of a variety of policies and institutions that relocate production factors from high to low TFP firms. Several examples of such policies include size-dependent taxes and subsidies, selective enforcement of regulations, financial constraints, poor enforcement of contracts, and internal trade costs, among others. This approach has been widely used in the misallocation literature, for instance, by \citet{HsiehKlenow:2009, HsiehKlenow:2014}, \citet{Bartelsmanetal:2013}, \citet{AdamopoulosRestuccia:2014}, and \citet{BentoRestuccia:2016}, among others.}%\footnote{Here we take the so-called \emph{indirect} approach in the study of misallocation (\citet{RestucciaRogerson:2013}), and quantify the overall effects of misallocation without identifying the specific underlying sources of the misallocation, such as size-dependent taxes and subsidies, selective enforcement of regulations, financial constraints, internal trade costs, and poor enforcement of contracts, among others. This approach has been widely used in the misallocation literature, for example, by \citet{HsiehKlenow:2009, HsiehKlenow:2014}, \citet{Bartelsmanetal:2013}, and \citet{AdamopoulosRestuccia:2014}, \citet{BentoRestuccia:2016} among others.}

%Moreover, we find that in China, the average product of labor and capital increase strongly with firm size and productivity [\citet{HsiehKlenow:2009, HsiehKlenow:2014}], suggesting the existence of size-dependent distortions.
% Specifically, if we take the U.S. economy as a relatively distortion-free benchmark, Fact 2 suggests that there could exist size-dependent distortions that reallocate factors away from large productive firms China, which we indeed find from the positive correlation between average factor product and firm level productivity [\citet{HsiehKlenow:2009, HsiehKlenow:2014}].\footnote{This measure of distortion captures the effects of many of the factors that distort factor allocation across firms, including taxes and subsidies, regulations, local protectionism, transportation costs, and financial frictions. A prominent example of such size-dependent distortions is internal trade barriers that impede the flow of goods across regions, which presumably affect large firms more since these are more likely to sell goods across regions [\citet{Young:2000}, \citet{TombeZhu:2015}, and \citet{Eberhardtetal:2016}]. In addition, as is the case in many other developing countries, small firms are more likely to evade taxes because of imperfect tax enforcement.} The literature has found that size-dependent distortions limit the operations of large productive firms and allow too many small unproductive firms to survive, which lowers both mean firm size and aggregate output.\footnote{See for instance \citet{Guneretal:2008}, \citet{Bartelsmanetal:2013}, \citet{HsiehKlenow:2014}, and \citet{BentoRestuccia:2016} among others.}
% An additional insight that we provide in this study is that size-dependent distortions also increase aggregate pollution intensity for two reasons. First, they lower the profits of firms which makes clean technology investment unaffordable to many firms. Second, they reduce the factors allocated to large productive firms which are more likely to use advanced pollution treatment technologies, and therefore reduce the share of total output that is produced using clean technologies. However, since size-dependent distortions both increase aggregate pollution intensity and reduce aggregate output, it is a quantitative question whether they also amplify aggregate pollution.

% To guide our analysis, we use a quantitative model to organize our empirical findings as well as quantifying the effects of size-dependent distortions on aggregate output and pollution. In particular, we extend the classic \citet{Lucas:1978b} span-of-control model to include a distinction between polluting and non-polluting sector, size-dependent distortions, an endogenous choice of pollution treatment technologies, and imperfect environmental regulations. In our model, there is a stand-in household with a continuum of members. Household members are endowed with different sectoral specific managerial talents and make occupational choices based on their talents. If a member chooses to be an entrepreneur, s/he uses her managerial talent (which becomes the firm-level productivity), capital, and labor to produce the output in the sector where the managerial talent belongs. S/he also has to pay implicit taxes that depend on her talent, which aims to capture size-dependent distortions in an intuitive way. Firm size is therefore determined by the managerial talent and distortions jointly.

% A novel feature of our model is that firms in the polluting sector also make decisions on pollutants treatment technologies. The installation of clean technology incurs a fixed cost and we assume that firms without clean technology will lose a fraction of their profits, capturing various regulatory costs that firms using dirty technology face parsimoniously. The fixed costs associated with the installation of clean technology lead to increasing returns to scale, which implies that only firms above a certain size threshold choose to install the clean technology in our model. For a given distribution of managerial talents and distortions, the model generates endogenously a distribution of firm sizes and a negative association between firm size and pollution intensity. To discipline our quantitative analysis, we require our benchmark model to match the observed pollution intensity, clean technology adoption rate, size-dependent distortions, and firm size distribution in China. %Distortions in the model is measured using variations in average products of capital and labor across firms following \citet{HsiehKlenow:2009, HsiehKlenow:2014}.

>>>>

% AEJ-Article.tex for AEA last revised 22 June 2011
\documentclass[AEJ]{AEA}

% The mathtime package uses a Times font instead of Computer Modern.
% Uncomment the line below if you wish to use the mathtime package:
%\usepackage[cmbold]{mathtime}
% Note that miktex, by default, configures the mathtime package to use commercial fonts
% which you may not have. If you would like to use mathtime but you are seeing error
% messages about missing fonts (mtex.pfb, mtsy.pfb, or rmtmi.pfb) then please see
% the technical support document at http://www.aeaweb.org/templates/technical_support.pdf
% for instructions on fixing this problem.

% Note: you may use either harvard or natbib (but not both) to provide a wider
% variety of citation commands than latex supports natively. See below.

% Uncomment the next line to use the natbib package with bibtex
\usepackage{natbib}

% Uncomment the next line to use the harvard package with bibtex
%\usepackage[abbr]{harvard}

% This command determines the leading (vertical space between lines) in draft mode
% with 1.5 corresponding to "double" spacing.
\draftSpacing{1.5}
\usepackage{natbib, graphicx, amssymb, epstopdf}
% To the editor: booktabs is only used for \cmidrule in tables 4 and 6.
\usepackage{enumerate, booktabs}

\newcommand{\E}{\mathbb{E}}
\newcommand{\e}{\mathrm{e}}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\plim}{plim}
\renewcommand{\vec}[1]{\ensuremath{\mathbf{#1}}}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}

\begin{document}

\title{The Size Distribution of Firms and Industrial Water Pollution \\ A Quantitative Analysis of China}
\shortTitle{FIRM SIZE DISTRIBUTION AND POLLUTION}
\author{Ji Qi, Xin Tang, and Xican Xi\thanks{%
Qi: Chinese Academy for Environmental Planning, Room 709-B BeiKeChuangYe Tower, No.10 Dayangfang, Beiyuan Road, Beijing, China, 100012 (e-mail: qiji@caep.org.cn); Tang: Wuhan University and International Monetary Fund, 700 19th St NW, Washington D.C., United States, 20431 (e-mail:zjutangxin@gmail.com); Xi: School of Economics, Fudan University, 600 Guoquan Road, Shanghai, China, 200433 (e-mail:xicanxi@fudan.edu.cn). We are grateful for the comments from Alexis Anagnostoupolos, Marina Azzimonti, Juan Carlos Conesa, Berthold Herrendorf, Nicolai Kuminoff, Pietro Peretto, Edward Prescott, Diego Restuccia, Todd Schoellman, Kerry Smith, Daniel Yi Xu, Gustavo Ventura, the editor and three anonymous referees. We also benefited from the comments received at Arizona State University, the Chinese Academy of Environmental Planning, Duke University, the IMF, U.S International Trade Commission, Peking University, Shanghai University of Finance and Economics, Singapore Management University, Stony Brook University, Washington State University, Wuhan University, and Zhejiang University. We sincerely thank the China Ministry of Ecology and Environment for granting us access to the National General Survey of Pollution Sources data. This paper has been screened to ensure that no confidential data are revealed.}}
\date{\today}
\pubMonth{Month}
\pubYear{Year}
\pubVolume{Vol}
\pubIssue{Issue}
\JEL{E23, L11, O44, Q52, Q53, Q56}
\Keywords{Firm Size Distribution, Correlated Distortion, Industrial Water Pollution}

\begin{abstract}
    We argue that misallocation across firms amplifies industrial water pollution by distorting the firm size distribution in China. Firm-level data indicate that larger firms are more likely to use clean technology but face higher distortions. In a heterogeneous firms model with an endogenous choice of pollution treatment technologies, we show that distortions that increase with firm-level TFP lower the adoption of clean technology, amplify aggregate pollution intensity, and lower aggregate output. Quantitatively, eliminating these correlated distortions would increase output by 30\% and decrease pollution by 20\%. Meanwhile, environmental regulations have sizable impact on pollution but only limited effect on output.
\end{abstract}

\maketitle

Severe pollution has accompanied China's remarkable economic growth in the past few decades, causing environmental degradation, public health damage, and millions of premature deaths.\footnote{\citet{WorldBank_Cost_2007} estimates that the cost of air and water pollution in China is about 6\% of GDP. The health cost of pollution is estimated to be 4\% of GDP, the majority of which is associated with premature deaths caused by pollution. See \citet{Vennemoetal:2009} and \citet{ZhengKahn:2013} for review of empirical studies on environmental pollution in China.} Understanding the driving forces behind this severe pollution is crucial for designing and evaluating anti-pollution policies. An outstanding question is whether the severe pollution is an inevitable consequence of rapid economic growth, or largely exacerbated by policy distortions and/or market inefficiencies.

In this paper, we argue that misallocation across firms amplifies industrial water pollution by distorting the firm size distribution in China. Using nationally representative data on firm production, pollution emissions and pollution treatment technologies, we document two facts on firm size and pollution intensity (pollutants per output) in China.\footnote{We use the \textit{National General Survey of Pollution Sources} (NGSPS) and \textit{National Economic Census} (CNEC) in China. Section I provides more details.} First, large firms have lower pollution intensity than small firms, with an elasticity of $-$0.37 between firm size and pollution intensity for the top five polluting industries in China.\footnote{The industries are ranked by their emissions of \textit{Chemical Oxygen Demand} (COD). The five industries are (with two-digit GB/T4547-2002 code in parentheses): Paper and Paper Products (C22), Processing of Food from Agricultural Products (C13), Textiles (C17), Raw Chemical Materials and Chemical Products (C26), and Beverages (C15).} Furthermore, we find that this is not only due to fewer pollutants per output are generated by large firms during production, but also that large firms are also more likely to use advanced end-of-pipe treatment technologies that require sizable fixed installation costs. Second, large firms account for a smaller proportion of the total employment in China than in the United States. For the top five polluting industries in China, firms with more than 400 employees account for 20\% of the total employment compared with close to 70\% for the U.S. counterparts. If we take the U.S. economy as a less distorted benchmark, these facts suggest that distortions to firm size distribution could have important environmental consequences in China.

Motivated by these facts, we build a two-sector (polluting and non-polluting) model of heterogeneous firms based on \citet{Lucas:1978b} to evaluate how firm-level distortions affect aggregate output and pollution. The model has the following key features. First, firms in each sector differ in their productivity levels. There is a stand-in household with a continuum of members, and each member draws a sector specific managerial ability from a given distribution. When members choose to be manager, they enter the sector their managerial ability belongs to and the ability determines the TFP of the firm they run. Second, firms differ in pollution intensity as well. As in \citet{CopelandTaylor:1994}, pollution emissions are a by-product of production for firms in the polluting sector. Following Fact 1 above, we assume that generated emissions per output during production is decreasing in firm output.\footnote{While our data reveal that large firms generate fewer pollutants per output, we do not know precisely the reasons behind that. Without further data, we model the emissions generated during production in a reduced-form way, which is then calibrated to the data. Section I.B discusses this point in more details.} Third, firms have the option to adopt an advanced end-of-pipe treatment technology, which we refer to as \textit{clean} technology later, after paying a fixed adoption cost. Firms in the polluting sector are subject to environmental regulations such that firms that do not use the clean technology face a penalty that takes away a fraction of their profits. As a result, our model predicts that only firms above a certain size threshold would choose the clean technology, which is qualitatively consistent with the fact that large firms are more likely to use clean technology.

Finally, we assume that firms face distortions that increase with their TFP, or \textit{correlated} distortions following the terminology of \citet{RestucciaRogerson:2008}, which are modeled as progressive output taxes.\footnote{\citet{Guneretal:2008} study a closely related type of distortions, namely \textit{size-dependent} distortions, which increase with firm or establishment size (the amount of capital, labor or output). An example is the many labor regulations in Italy, Spain and France that start to bind on firms with more than a certain number of employees. Both correlated and size-dependent distortions lead to a reallocation of resources from high TFP to low TFP firms, and they are essentially equivalent when distortions do not lead to rank reversal defined as more productive firms being smaller [\citet{Hopenhayn:2014}].} We find in our data that firms with higher TFP exhibit substantially higher average products of capital and labor in both the polluting and non-polluting sectors, indicating that more productive firms do face higher distortions [\citet{HsiehKlenow:2009, HsiehKlenow:2014}]. As emphasized by previous studies, such as \citet{RestucciaRogerson:2008} and \citet{HsiehKlenow:2014}, correlated distortions lower both mean firm size and aggregate output, since they limit the operations of productive firms and allow too many unproductive firms to survive and expand. A new insight from our model is that correlated distortions also increase aggregate pollution intensity for two reasons. First, they lower the profits of productive firms which reduces their incentives to adopt the clean technology. Therefore fewer firms adopt clean technology in the equilibrium with correlated distortions. Second, they take production factors away from large productive firms that also have lower pollution intensity, which drives up the average pollution intensity further.

@@

To discipline our quantitative analysis, we calibrate our model to match the observed pollution intensity, the adoption of clean technology, the correlation between distortions and firm TFP, and the firm size distribution in the Chinese data. We map the polluting sector to the top five polluting industries mentioned above, which account for 80\% of the total emissions in the data, and map the non-polluting sector to the rest of the manufacturing sector. We then use the calibrated model to evaluate the effects of two policies: removing correlated distortions from both sectors and strengthening environmental regulations.\footnote{Here we follow the so-called \textit{indirect} approach in the study of misallocation [\citet{RestucciaRogerson:2013}] by quantifying the overall effects of a variety of policies and institutions that relocate production factors from high to low TFP firms. Several examples of such policies include size-dependent taxes and subsidies, selective enforcement of regulations, financial constraints, poor enforcement of contracts, and internal trade costs, among others. This approach has been widely used in the misallocation literature, for instance, by \citet{HsiehKlenow:2009, HsiehKlenow:2014}, \citet{Bartelsmanetal:2013}, \citet{AdamopoulosRestuccia:2014}, and \citet{BentoRestuccia:2016}, among others.}

Our quantitative results show that removing correlated distortions from both sectors would increase mean firm size by 130\% and aggregate output by 30\%, while lowering the pollution intensity of the polluting sector by 42\%. Since both sectors share similar distributions of firm TFP and distortions in the data, eliminating correlated distortions induces little reallocation across sectors. Therefore, aggregate pollution drops by 23\% because the technique effect dominates the scale effect. About half of the technique effect comes from the reallocation of factors across firms, while the rest is from a 27 percentage points increase in the adoption rate of clean technology. To isolate the importance of the \textit{progressivity} of distortions, we solve a version of the model in which the progressive taxes are replaced with flat taxes while holding the total tax revenue constant. Our results show that while the progressivity of distortions does not imply large output losses (7\%), it plays a central role in amplifying aggregate pollution (30\%).

In the second experiment, we increase the regulations to the extent that the fraction of firms adopting clean technology is the same as in the first experiment. We find that the policy reduces aggregate pollution by 14\%, but has very limited effect on aggregate output in the long run. Comparing this with the first experiment, we find that tightening environmental regulations {improves} the resource allocation on the \textit{extensive} margin of resource allocation by driving small unproductive firms out of the economy. However, the allocation {worsens} on the \textit{intensive} margin in the sense that among the remaining active firms, the production of medium-sized firms expands more at the expense of that of large firms. In contrast, the removal of correlated distortions improves the allocation on both margins.
